---
title: "Simulation Follow-up Studies"
output: 
    html_document:
      code_download: TRUE
      toc: TRUE
      toc_float:
        collapsed: FALSE
      toc_depth: 1
      code_folding: hide
      mathjax: null
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE, warning = FALSE, message = FALSE, error = FALSE}
library(simr)
library(lme4)
library(tidyr)
library(dplyr)
#library(tidyverse)
#library(magrittr)
library(rio)
library(sjPlot)

source("functions/Cleaning.R")

# Setting global chunk options
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

options(scipen = 999)

# Importing data
wide_raw <- import("data/analog2_wide_pt to remove.csv") 

# Cleaning data using functions
wide_data_clean <- wide_factor_clean(wide_raw)

long_data <- wide_to_long(wide_data_clean)

study1_data <- long_data %>% 
  select(sub_id, target_bfi_value, target_bfi_number, self_c, 
         target_number_collapsed, condition_order, threat_c, cand_pref, threat) %>% 
  filter(cand_pref == "Not Trump Supporter") %>% 
  na.omit() %>% 
  unique()

study1_filtered <- study1_data %>% 
  filter(target_number_collapsed == "target_1")
```

# Using data from Study 1 (observed power) {.tabset .tabset-fade .tabset-pills}

**These reflect observed power of results that can be found in Study 1 of my dissertation (project titled analogous-perspective-taking-2 on github: https://github.com/kdenning/analogous-perspective-taking-2). I am using them here as reference for simulations for Studies 2 and 3 below.**

## 2 categorical & self

```{r}
study1_mod1 <- lmer(target_bfi_value ~ self_c*target_number_collapsed*condition_order + (self_c|sub_id), data = study1_data)

tab_model(study1_mod1)

powerSim(study1_mod1, test = fcompare(target_bfi_value ~ self_c:target_number_collapsed:condition_order), nsim = 10)

study1_mod2 <- lm(threat ~ target_number_collapsed*condition_order, data = study1_data)

tab_model(study1_mod2)

# pre-ratings of threat were higher for order 1 (female first) than order 2
ggplot(study1_data, aes(condition_order, threat)) +
  geom_col() # weird, hadn't even seen a target yet...
```

```{r}
study1_filter_mod1 <- lmer(target_bfi_value ~ self_c*condition_order + (self_c|sub_id), data = study1_filtered)
tab_model(study1_filter_mod1)

library(tidyverse)
ggplot(study1_filtered, aes(self_c, target_bfi_value, group = condition_order)) +
  geom_smooth(method = "lm")
```

## Adding moderator

```{r}
study1_mod2 <- lmer(target_bfi_value ~ self_c*target_number_collapsed*condition_order*threat_c + (self_c|sub_id), data = study1_data)

powerSim(study1_mod2, test = fcompare(target_bfi_value ~ self_c:target_number_collapsed), nsim = 10)
```

# Simulated power - Study 2 {.tabset .tabset-fade .tabset-pills}

```{r}
targ_conditions <- c("pre/post", "warm male", "warm female", "cold female")
intervention <- c("analog", "analog", "analog", "analog", "control", "control", "control", "control")

psych::describe(long_data$self_c)
psych::describe(long_data$target_bfi_value)
psych::describe(long_data$threat_c)
# stereo from Denning & Hodges (2021) exploratory supplemental materials for the confirmatory experimental 0 for centering, 1.22 for SD
# ELI for stereo SD 1.02, mean 0 for centering
# ELI for self?
# ELI for targ?

sim_bfi_df <- data.frame(id = rep(factor(1:1000), each = 19),
                     bfi_num = rep(factor(1:19)),
                     targ = rep(rnorm(19000, mean = 3, sd = 1.14)),
                     self = rep(rnorm(19000, mean = 0, sd = 1.28)),
                     stereo = rep(rnorm(19000, mean = 0, sd = 1.22)),
                     threat = rnorm(19000, mean = 0, sd = 1.3),
                     targ_condition = factor(rep(targ_conditions, each = 19)),
                     intervention = factor(rep(intervention, each = 19)))

sim_bfi_df %>% 
  group_by(targ_condition, intervention) %>% 
  count()
```

## BFI Simulation Model

```{r}
tab_model(study1_mod1) # Using results from study 1 as basis

my.helmert = matrix(c(-1/4, 3/4, -1/4, -1/4, 2/3, 0, -1/3, -1/3, 0, 0, 1/
	2, -1/2), ncol = 3)
my.helmert

contrasts(sim_bfi_df$targ_condition) = my.helmert
contrasts(sim_bfi_df$targ_condition)

# fixed <- c(3, 0.09, 0.2, 0.01, 0.15, 0.10, 0.03, 0.10, 0.10, 0.20, 0.15, 0.10, 0.15, 0.10, 0.0, 0.0, 0.0, 0.0, 0.0, 0.15, 0.10, 0.03, 0.15, 0.10, 0.05, 0.10, 0.20, 0.15, 0.10, 0.20, 0.15, 0.10, 0.15, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0)

fixed <- c(3, 0.09, 0.10, 0.01, 0.08, 0.06, 0.03, 0.10, 0.10, 
           0.2, 0.15, 0.10, 0.05, 0.15, 
           0.08, 0.05, 0.03, 0.10, 0.08, 0.04, 0.10,
           0.10, 0.08, 0.04, 0.10, 0.08, 0.05, 0.10,
           0.0, 0.0, 0.0, 0.0, 0.0,
           0.10, 0.08, 0.04, 0.10, 0.06, 0.02,
           0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.05, 0.03, 0.01)
# fixed <- c(3, -0.10, 0.03, 0.10, 0.15, 0.01, -0.05, -0.35)
rand <- list(.02, .06, .55) # Use values on the between subjects model in Denning & Hodges 2021
res <- 8.5 # For between-subjects was .91; using higher value to be more conservative

# checking moderating relationship without stereo and with stereo in the same model to account for stereotyping; not allowing interactions of variables without stereo or self as they are not relevant
sim_mod1 <- makeLmer(targ ~ self + stereo + self:stereo +
                       self:targ_condition + self:intervention + self:threat +
                       self:targ_condition:intervention +
                       self:targ_condition:threat + self:intervention:threat +
                       self:targ_condition:intervention:threat +
                       stereo:targ_condition + stereo:intervention + stereo:threat +
                       stereo:targ_condition:intervention +
                       stereo:targ_condition:threat + stereo:intervention:threat +
                       stereo:targ_condition:intervention:threat +
                       self:stereo:targ_condition + self:stereo:intervention +
                       self:stereo:threat +
                       self:stereo:targ_condition:intervention +
                       self:stereo:targ_condition:threat + 
                       self:stereo:intervention:threat +
                       self:stereo:targ_condition:intervention:threat
                       
 + (self|id), fixef=fixed, VarCorr = rand, sigma = res, data = sim_bfi_df)

tab_model(sim_mod1)


```

### Powercurve

*Accounting for stereotyping but not interacting*

```{r}
powercurve_sim1 <- powerCurve(sim_mod1, 
                                  along = "id", 
                                  nsim = 100,  
                                  test = fcompare(targ ~ self:targ_condition:intervention:threat),
                                  breaks = c(400, 500, 550, 600, 650, 700))
powercurve_sim1

plot(powercurve_sim1)

# https://cran.r-project.org/web/packages/simr/vignettes/examples.html
```
